Marlowe: implementing and analysing financial contracts\thanks{Supported by IOHK.}

### 2019-12-05 papers/marlowe2019/paper.tex
Fix SBV example

\begin{verbatim}
primeFactors :: SBV Integer -> SBV Integer -> SBV Bool
primeFactors x y = x .> 1 .&& y .> 1 .=> x * y ./= 25723297
\end{verbatim}

@@

\begin{verbatim}
*Main> primeFactors 98 314
True
*Main> prove primeFactors
Falsifiable. Counter-example:
    s0 = 6353 :: Integer
    s1 = 4049 :: Integer
*Main> primeFactors 6353 4049
False
\end{verbatim}

>>>>

\begin{verbatim}
primeFactors :: SBV Integer -> SBV Integer -> SBV Bool
primeFactors x y = x .> 1 .&& y .> 1 .&& x * y .== 25723297
\end{verbatim}

@@

\begin{verbatim}
*Main> primeFactors 98 314
False
*Main> sat primeFactors 
Satisfiable. Model:
    s0 = 6353 :: Integer
    s1 = 4049 :: Integer
*Main> primeFactors 6353 4049
True    
\end{verbatim}
